\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-14 report/paper.tex
changed cell list image, writingt on cellist

\documentclass[12pt, twocolumn]{article}

% Our packages
\usepackage{graphicx}   % Images
\usepackage{amsmath}    % Math
\usepackage{amssymb}    % Math
\usepackage{listings}   % To write code in latex
\usepackage{color}      % Custom colors

@@

\begin{lstlisting}[language=C++, mathescape=true, escapeinside={(*}{*)}]
function performSimulation
    for all particles $i$ do //Init neighbourhoods
        find neighbourhoods $N_i(0)$
    for all particles $i$ do //Init $\color{codegreen}\rho_i$ and $\color{codegreen}\alpha_i$
        compute densities $\rho_i(0)$
        compute factors $\alpha_i(0)$
    while (t < $t_{max}$) do //Start simulation loop
        adapt time step $\Delta{t}$ 
        for all particles $i$ do //Predict velocities $\color{codegreen}\mathbf{v}_i^*$
            $\mathbf{v}_i = \mathbf{v}_i + \Delta{t}\mathbf{F}_i^{adv}/m_i$
        correctDensityError($\alpha, \mathbf{v}_i$) //Fulfill $\color{codegreen}\rho^* - \rho_0 = 0$
        for all particles $i$ do //Update positions
            $x_i(t + \Delta{t}) = x_i(t) + \Delta{t}\mathbf{v}_i^*$
        for all particles $i$ do //Update neighbourhoods
            find neighbourhoods $N_i(t + \Delta{t})$
        for all particles $i$ do //Update $\color{codegreen}\rho_i$ and $\color{codegreen}\alpha_i$ 
            compute densities $\rho_i(0)$
            compute factors $\alpha_i(0)$
        correctDivergenceError($\alpha, \mathbf{v}^*$) //Fulfill $\color{codegreen}\frac{D\rho}{Dt} = 0$
\end{lstlisting}

\subsection{Neighbourhood search}
    Since SPH only considers a finite amount of neighbouring particles, it is important to keep track of every particles neighbours.
    Searching through all particles for neighbours within the cutoff distance $H$ for every particle is inefficient and takes $\mathcal{O}({N^2})$ time.
    The cutoff distance $H$ is the kernel smoothing radius.
    To fasten this up a cell list was implemented.
    A cell list is a data structure that is divided into cells that have a length larger or equals to the cutoff distance $H$.
    When finding the neighbour of particle $i$, only the neighbouring cells have to be searched for particles within the cutoff distance, see figure~\ref{fig:cellList}.

    \begin{figure}
    \includegraphics[width=\linewidth]{img/CellLists2.png}
    \caption{Finding the neighbours for the filled in particle $i$ by looking through all neighbouring cells, including its own cell, for particles within the cutoff distance $H$}
    \label{fig:cellList}
    \end{figure}

    The cell list is implemented by using a four dimensional vector where the first three dimensions are for the x, y and z coordinates for the cells and the fourth dimension is for storing the particles belonging to the cell.
    The amount of cells are decided by dividing the scene into cells of length $H$.
    The particles are then assigned to a cell according to Equation ~\ref{eq:assignCell}.
    If the particle moves out of its cell it is then assigned to the new cell.

    \begin{equation} \label{eq:assignCell}
        sjdfkljsf
    \end{equation}

>>>>

\documentclass[11pt, twocolumn]{article}

% Our packages
\usepackage{graphicx}   % Images
\usepackage{amsmath}    % Math
\usepackage{amssymb}    % Math
\usepackage{listings}   % To write code in latex
\usepackage{color}      % Custom colors
\usepackage{abstract}   % Onecolabstract, saythanks
\usepackage[margin=1.2in]{geometry}

\setlength{\columnsep}{20px} % Length between twocolumn

@@

\begin{lstlisting}[language=C++, mathescape=true, escapeinside={(*}{*)}]
function performFluidSimulation
    for all particles $i$ do //Init neighbourhoods
        find neighbourhoods $N_i(0)$
    for all particles $i$ do //Init $\color{codegreen}\rho_i$ and $\color{codegreen}\alpha_i$
        compute densities $\rho_i(0)$
        compute factors $\alpha_i(0)$
    while (t < $t_{max}$) do //Start simulation loop
        adapt time step $\Delta{t}$ 
        for all particles $i$ do //Predict velocities $\color{codegreen}\mathbf{v}_i^*$
            $\mathbf{v}_i = \mathbf{v}_i + \Delta{t}\mathbf{F}_g/m_i$
        correctDensityError($\alpha, \mathbf{v}_i$) //Fulfill $\color{codegreen}\rho^* - \rho_0 = 0$
        for all particles $i$ do //Update positions
            $x_i(t + \Delta{t}) = x_i(t) + \Delta{t}\mathbf{v}_i^*$
        for all particles $i$ do //Update neighbourhoods
            find neighbourhoods $N_i(t + \Delta{t})$
        for all particles $i$ do //Update $\color{codegreen}\rho_i$ and $\color{codegreen}\alpha_i$ 
            compute densities $\rho_i(0)$
            compute factors $\alpha_i(0)$
        correctDivergenceError($\alpha, \mathbf{v}^*$) //Fulfill $\color{codegreen}\frac{D\rho}{Dt} = 0$
\end{lstlisting}

\subsection{Neighbourhood search}
    Since SPH only considers a finite amount of neighbouring particles it is important to keep track of every particles neighbours.
    Searching through all particles for neighbours within the cutoff distance $H$ for every particle is inefficient and takes $\mathcal{O}({N^2})$ time.
    The cutoff distance $H$ is the kernels smoothing radius.
    To make this faster a cell list was implemented.
    A cell list is a data structure that is divided into cells that have a length larger or equals to the cutoff distance $H$.
    Each cell spans on a surface in space.
    A particle belongs to a cell if it is inside the space the cell occupy.
    When finding the neighbour of particle $i$, only the neighbouring cells have to be searched for particles within the cutoff distance, see figure~\ref{fig:cellList}.

    \begin{figure}[h!]\centering
    \begin{centering}
    \includegraphics[width=0.7\linewidth]{img/CellList.png}
    \caption{Finding the neighbours for the filled in particle $i$ by looking through all neighbouring cells, including its own cell, for particles within the cutoff distance $H$}
    \label{fig:cellList}
    \end{centering}
    \end{figure}

    The cell list is implemented by using a four dimensional vector where the first three dimensions are for the x, y and z coordinates and the fourth dimension is for storing the particles belonging to the cell.
    The amount of cells are decided by dividing the scene into cells of length $H$.
    The particles are then assigned to a cell by finding the cell's coordinates that it belongs to according to Equation ~\ref{eq:assignCell}, where $vect{x}$ is the position of the particle and $vect{s}_min$ is the lowest position in the scene space.
    If the particle moves out of its cell it is reassigned to the new cell it is inside.

    \begin{equation} \label{eq:assignCell}
        \frac{\lceil{pos - s_{min}}\rceil}{H}
    \end{equation}
